Your Title Goes Here

### 2018-01-05 documentation/documentation.tex

\paragraph{Tweepy}\mbox{}\\{}
Tweepy is a open-source libary. It provides a simple way to gather real time tweets, by managing authentication, connection and tweet information of Twitters streaming API. The tweepy instance tweepy.streaming is used for the streaming session and forwards the data to the StreamListener instance. The \verb|class listener(StreamListener)| calls the method \verb|def on_data(self, data)|. \parencite{tweepy} With this method all data of filtered tweets are gathered in real time. The main function \verb|def main()| manages the required authentication as follow:
\begin{lstlisting}[language=bash]
auth = OAuthHandler (ckey, csecret)
auth.set_access_token(atoken, asecret)
\end{lstlisting}
Those authentications are demanded by Twitter and explained in more details in the next paragraph. Furthermore, the main function starts the running of the stream, while filtering for the buzzword Bitcon by processing \verb|twitterStream.filter(track=["bitcoin"]|. Tweepy has been applied for this assignment because it simplify the script and enables to gather a huge number of tweets for free.

>>>>

\paragraph{Tweepy}\mbox{}\\{}
Tweepy is a open-source libary. It provides a simple way to gather real time tweets, by managing authentication, connection and tweet information of Twitters streaming API. The tweepy instance tweepy.streaming is used for the streaming session and forwards the data to the StreamListener instance. The \verb|class listener(StreamListener)| calls the method \verb|def on_data(self, data)|. With this method all data of filtered tweets are gathered in real time. \parencite{tweepy} The main function \verb|def main()| manages the required authentication as follow:
\begin{lstlisting}[language=bash]
auth = OAuthHandler (ckey, csecret)
auth.set_access_token(atoken, asecret)
\end{lstlisting}
Those authentications are demanded by Twitter and explained in more details in the next paragraph. Furthermore, the main function starts the running of the stream, while filtering for the buzzword Bitcon by processing \verb|twitterStream.filter(track=["bitcoin"]|. Tweepy has been applied for this assignment because it simplify the script and enables to gather a huge number of tweets for free.
